Notes on 10d Super Yang-Mills

### 2019-04-08 10d_SYM_Notes.tex
small edits

\newcommand{\C}{\mathbf{C}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}

\newcommand{\brian}[1]{\textcolor{blue}{BW: #1}}

@@

We can re-encode this data in terms of the classical BV complex (Phil and I wrote this down in \cite[Section 3.1]{ElliottYoo1}).  This is the $L_\infty$-algebra whose underlying cochain complex takes the form
\[\xymatrix{
\Omega^0(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{10}; \gg) \ar[r]^{\d \ast \d} &\Omega^9(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^{10}(\RR^{10}; \gg) \\
&\Omega^0(\RR^{10}; \Pi S_- \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S_- \otimes \gg), &
}\]
with degree $-3$ invariant pairing induced by the invariant pairing on $\gg$ and the pairing $(,)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
\begin{align*}
\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^0(\RR^{10}; S_{+} \otimes \gg) &\to \Omega^{10}(\RR^{10}; S_{-} \otimes \gg) \\
(A \otimes \lambda) &\mapsto \ast \sd A \lambda
\end{align*}
in degree 2, and the map
\begin{align*}
\ell_3 \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
\end{align*}
in degree 3.

@@

@@

\def\cN{\mathcal{N}}

>>>>

\newcommand{\C}{\mathbf{C}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}
\newcommand{\clie}{{\rm C}_{\rm Lie}}
\def\cN{\mathcal{N}}

@@

We can re-encode this data in terms of the classical BV complex (Phil and I wrote this down in \cite[Section 3.1]{ElliottYoo1}).  This is the $L_\infty$-algebra whose underlying cochain complex takes the form
\[\xymatrix{
\Omega^0(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{10}; \gg) \ar[r]^{\d \ast \d} &\Omega^9(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^{10}(\RR^{10}; \gg) \\
&\Omega^0(\RR^{10}; \Pi S_+ \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S_- \otimes \gg), &
}\]
\brian{I've changed the spinor component in degree zero to $S_+$, check if that's OK.}
with degree $-3$ invariant pairing induced by the invariant pairing on $\gg$ and the pairing $(,)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
\begin{align*}
\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^0(\RR^{10}; S_{+} \otimes \gg) &\to \Omega^{10}(\RR^{10}; S_{-} \otimes \gg) \\
(A \otimes \lambda) &\mapsto \ast \sd A \lambda
\end{align*}
in degree 2, and the map
\begin{align*}
\ell_3 \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
\end{align*}
in degree 3.

@@

\subsection{Off-shell supersymmetry action}

The goal is to show that the maps
\begin{align*}
\delta^{(1)}_+ \colon S_+ \otimes \left( \Omega^1(\RR^{10} ; \mf g) \oplus \Gamma(\RR^{10}; \Pi S_+[-1] \otimes \mf g) \right) &\to \Omega^1(\RR^{10} ; \mf g) \oplus \Gamma(\RR^{10}; \Pi S_+[-1] \otimes \mf g) \\
Q \otimes (A + \lambda) &\mapsto  \Gamma(Q,\lambda) + \sd F_A Q .
\end{align*}
\begin{align*}
\delta^{(2)}_+ \colon S_+ \otimes S_+ \otimes \Gamma(\RR^{10}; \Pi S_+) &\to \Gamma(\RR^{10}; \Pi S_-' [-1]) \\
Q_1 \otimes Q_2 \otimes \lambda &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
\end{align*}
define an $L_\infty$-action of the supersymmetry algebra on the BV complex.

The BV action involving the component $\Pi S_+$ of the supersymmetry algebra reads
\begin{align*}
I_+^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = A^* \wedge \Gamma(Q, \lambda) + (\lambda^*, \sd F_A Q) \\
I_+^{(2)} (Q_1,Q_2 ; \lambda^*) & = \pm \left(\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right) .
\end{align*}

\brian{Part of BV action involving the bosonic translations}

It suffices to show that the Maurer-Cartan equation for the functional $I^{(1)}_+ + I^{(2)}_+$ holds:
\[
(\d_{CE} + \d_{BV}) \left(I_+^{(1)} + I_+^{(2)}\right) + \frac{1}{2} \left\{I_+^{(1)} + I_+^{(2)}, I_+^{(1)} + I_+^{(2)} \right\} = 0 .
\]
The space of equivariant BV functionals $\clie^*(\mf g_{\cN=1}) \otimes \cO_{BV}$ is filtered by the number of anti-field components. 
With respect to this filtration,  this Maurer-Cartan equation splits into four equations:
\begin{enumerate}
\item[(1)] $\d_{BV} I^{(1)} = 0$ ;
\item[(2)] $\d_{CE} I^{(1)}_+ + \d_{BV} I^{(2)}_+ + \frac{1}{2}  \left\{I_+^{(1)} , I_+^{(1)} \right\} = 0$ ;
\item[(3)] $\d_{CE} I^{(2)}_+ + \{I^{(1)}_+, I^{(2)}_+\} = 0$ ;
\item[(4)] $\{I^{(2)}_+ , I^{(2)}_+ \} = 0$.
\end{enumerate}

Equation (1) follows from \brian{p. 14 in \cite{BaezHuerta}}.

Equation (2). \brian{this will entail adding a few sentences after Chris' calculation above.}

Equation (3).
Note that $\d_{CE} I^{(2)}_+ = 0$ since the term $I^{(2)}_+$ is quadratic in the term $\Pi S_+ \subset \mf g_{\cN =1}$ and there are no brackets that land in the odd component of supersymmetry algebra. 
The second term $\{I^{(1)}_+, I^{(2)}_+\}$ splits into two terms.
The first is a functional of the form \brian{keeping with Pavel's notation from the email, the $\Gamma_{\pm}$ and $\rho_{\pm}$ tell you which spinor your acting on}
\[
(Q_1, Q_2, Q_3 ; A^*, \lambda^*) \mapsto A^* \wedge \Gamma_+(Q_1, \rho_- (\Gamma_+(Q_2, Q_3)) \lambda^*) + (123)
\] 
and the second is
\[
(Q_1, Q_2, Q_3 ; A^*, \lambda^*) \mapsto (\lambda^*, Q_1) (A^* \wedge \Gamma_+(Q_2, Q_3)) + (123) .
\]

\begin{lemma}
For any $\psi_+ \in S_+$, $\psi_- \in S_-$, and $v \in V$, the following relation holds
\[
\Gamma_+(\psi_+, \rho_-(v) \psi_-) + \Gamma_-(\psi_-, \rho_+(v) \psi_+) = (\psi_-, \psi_+) v
\]
\end{lemma}
\begin{proof}
We will prove that for any $w \in V$ the following relation holds
\[
g\left(w, \Gamma_+(\psi_+, \rho_-(v) \psi_-) + \Gamma_-(\psi_-, \rho_+(v) \psi_+) \right) = (\psi_-, \psi_+) g(w,v)
\]
where $g$ is the fixed metric on $V$. 
Since \brian{Something about adjointness of $\Gamma$ and $\rho$} the left hand side is equal to
\[
\left(\rho(w) (\psi_+ + \psi_-), \rho(v) (\psi_+ + \psi_-) \right) .
\]
Now the pairing $(-,-) : S_{\pm} \otimes S_{\mp} \to \CC$ is equivariant with respect Clifford multiplication, so this is expression is equal to $g(w,v) (\psi_-, \psi_+)$ as desired.
Since this is true for all $w \in V$, the claim follows. 
\end{proof}

@@
